---
title: "Filter test data"
author: "Tim Ponton"
date: 
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(tidyverse)
library(ggplot2)
library(lubridate)
library(anytime)
library(dplyr)
library(reshape2)
library(data.table)
library(tidyr)
library(plotly)
library(patchwork)
library(vegan)
library(zoo)
```

```{r, include= FALSE}
options(scipen = 999)
df <- read.csv("Updated data from April 2020/Combo-as-of-April-2020-OpenRefineCopy.csv")

# fix date
df$Date <- as.Date(df$Date, "%d/%m/%Y")

# merge date and times and coerce to proper format 
df$dateTime <- as.POSIXct(paste(df$Date, df$Time), format = "%Y-%m-%d %H:%M")

```


```{r, include= FALSE}
# original df, summarise to daily total (i.e deal with two samples per day)
df_daily <- df %>% 
  group_by(Date, Site, Species, Classification) %>% 
  summarise(dailyCells = mean(Cells.L))

# Filter out where after drumfilter occurs to get days with >1 count site
df_daily_moreSite <- df_daily %>% 
  group_by(Date) %>% 
  filter("After Drumfilter" %in% Site)

# sum all cells
sum_df_daily_moreSite <- df_daily_moreSite %>% 
  group_by(Date, Site) %>% 
  summarise(TotalCells = sum(dailyCells))

# sum all cells
sum_df_daily_moreSite <- df_daily_moreSite %>% 
  group_by(Date, Site) %>% 
  summarise(TotalCells = sum(dailyCells))

# number of different sampling sites on a specific date
numberSites <- sum_df_daily_moreSite %>% 
  group_by(Date) %>% 
  summarise(n = n_distinct(Site))
```



When at least Primary sump and After Drumfilter have been sampeld on the same day
```{r, include= FALSE}
# subset dates where just 2 sites are present
TwoSiteClassify <- numberSites %>% 
  filter(n == 2)
# use dates as classifier to subset (And exclude December record)
TwoSite <- sum_df_daily_moreSite %>% 
  filter(Date %in% TwoSiteClassify$Date) %>% 
  filter(Date != "2019-12-17")
```

```{r, echo= FALSE, message=FALSE, warning=FALSE}

ggplot(data = TwoSite, aes(x = Date, y = TotalCells, fill = Site)) +
  geom_bar(stat = "Identity", position = "Dodge")

```




The percentage difference of cells counted after the drumfilter after being counted in primary sump i.e how well do the drum filters filter out cells
```{r, include= FALSE}

wide_TwoSite <- TwoSite %>% 
  pivot_wider(names_from = Site, values_from = TotalCells)

 #calculate percentage of afterdrum to primary counts
percentage <- wide_TwoSite %>% 
  mutate(PercentDrumFilter = (`After Drumfilter`/`Primary sump`)*100) %>% 
  mutate(MoreDrum = ifelse(`After Drumfilter` > `Primary sump`, "Greater", "Less"))
```

```{r, echo= FALSE, message=FALSE, warning=FALSE}
ggplot(data = percentage, aes(x = Date, y = PercentDrumFilter)) +
  geom_point() +
  geom_line() +
  geom_hline(yintercept = 100, linetype="dashed", color = "red")

```





Total cells collected from different points on the farm on the 2019-02-26, where the most sites were sampled

```{r, echo= FALSE, message=FALSE, warning=FALSE}


mostSiteClassify <- numberSites %>% 
  filter(n > 10)

mostSites <- df_daily %>% 
  filter(Date %in% mostSiteClassify$Date) %>% 
  group_by(Date, Site) %>% 
  summarise(totalCells = sum(dailyCells))

```



Total cells collected from different points on the farm on the 2019-02-12, where 2nd most sample sites were visited

```{r, echo= FALSE, message=FALSE, warning=FALSE}
df %>% 
  filter(Date == "2019-02-12") %>% 
  group_by(Site) %>% 
  summarise(meanCells = mean(Cells.L)) %>% 
  ggplot(., aes(x = reorder(Site, -meanCells), y = meanCells)) +
  geom_bar(stat = "Identity", position = "Dodge") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) 
```



```{r, echo= FALSE, message=FALSE, warning=FALSE}
mostSites %>% 
    filter(Date == "2019-02-26") %>% 
    ggplot(., aes(x = reorder(Site, -totalCells), y = totalCells)) + 
    geom_bar(stat = "Identity") +
    scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

Counts at different times on the 2019-03-19 at Primary sump and after drumfilter

```{r, echo= FALSE, message=FALSE, warning=FALSE}
df %>% 
  filter(Date == "2019-03-19") %>% 
  ggplot(., aes(x = Time, y = Cells.L, fill = Site)) +
  geom_bar(stat = "Identity", position = "Dodge") +
    scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

Fine scale line graph of totals cells counted Primary sump and after drumfilter for several consecutive days, where sampling occurred multiple times a day


```{r, echo= FALSE, message=FALSE, warning=FALSE}
big <- df %>% 
  filter(Date >= as.Date("2019-03-18") & Date <= as.Date("2019-03-27")) %>% 
  filter(Site %in% c("Primary sump", "After Drumfilter")) %>% 
  group_by(dateTime, Site) %>% 
  summarise(totalCells = sum(Cells.L))


ggplotly(ggplot(data = big, aes(x = dateTime, y = totalCells, col = Site)) +
  geom_line())
```




The difference in average Cells/L found After the Drumfilter compared to Primary sump

```{r, echo= FALSE, message=FALSE, warning=FALSE}
#### what species occur when after drumfilter > primary filter ####

ggplotly(df %>% 
  group_by(Date) %>% 
  filter(Classification != "Various", Date != "2019-12-17", Date != "2019-02-17") %>% 
  filter(all(c("After Drumfilter", "Primary sump") %in% Site)) %>% 
  filter(Site %in% c("After Drumfilter", "Primary sump")) %>% 
  ungroup() %>% 
  group_by(Date, Site, Species) %>% 
  summarise(meanC = mean(Cells.L, na.rm = TRUE)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = Site, values_from = meanC, 
              values_fill = list(meanC = 0)) %>% 
  group_by(Date, Species) %>% 
  filter(`After Drumfilter` > `Primary sump`, `Primary sump` != 0) %>% 
  mutate(difference = `After Drumfilter` - `Primary sump`) %>% 
  group_by(Species) %>% 
  summarise(totalMean = mean(difference)) %>% 
  ggplot(., aes(x = reorder(Species, totalMean), y = totalMean)) +
    geom_point() +
    coord_flip())
```


  

When times are rounded off, a look at two consecutive days, where multiple samples are taken throughtout the time period, and the difference in time from original to rounded off for each time period


```{r, echo= FALSE, message=FALSE, warning=FALSE}

# round off time to certain amount
df$roundTime <- round_date(df$dateTime, "2 hour")

a <- df %>% 
  group_by(Date) %>% 
  filter(Classification != "Various", Date != "2019-12-17", Date != "2019-02-17") %>% 
  filter(all(c("After Drumfilter", "Primary sump") %in% Site)) %>% 
  filter(Site %in% c("After Drumfilter", "Primary sump")) %>%
  mutate(timeDiff = (dateTime - roundTime)/60) %>% 
  ungroup() %>% 
  group_by(roundTime, Site) %>% 
  summarise(totalCells = sum(Cells.L)) %>%
  filter(roundTime >= as.Date("2019-02-19") & roundTime <= as.Date("2019-02-20")) %>% 
  ggplot(., aes(x = roundTime, y = totalCells, fill = Site)) +
  geom_bar(stat = "Identity", position = "Dodge")



b <- df %>% 
  group_by(Date) %>% 
  filter(Classification != "Various", Date != "2019-12-17", Date != "2019-02-17") %>% 
  filter(all(c("After Drumfilter", "Primary sump") %in% Site)) %>% 
  filter(Site %in% c("After Drumfilter", "Primary sump")) %>%
  mutate(timeDiff = (dateTime - roundTime)/60) %>% 
  filter(roundTime >= as.Date("2019-02-19") & roundTime <= as.Date("2019-02-20")) %>% 
  ggplot(., aes(x = roundTime, y = timeDiff, fill = Site)) +
  geom_bar(stat = "Identity", position = "Dodge", col = "black") +
  geom_hline(yintercept = 0, color = "black")


a/b   

```


